This thesis has been nothing if not a labor of love.
As with all such endeavors, there have been many ups and many downs along the way and I cannot imagine completing my PhD without the love and support of my wonderful mentors, collaborators, friends and family.

First and foremost, I would like to thank my adviser, Percy Liang, whose energy, breadth of knowledge and on-point advice have nutured my growth as a researcher, professional and person immensely.
I've had the distinct privilege of being able to pursue research agendas in both machine learning theory and natural language processing and I can't imagine another person with whom this would have been possible.
By no means have I been an easy graduate student to advise, and yet Percy took it in his stride.
To Percy: for all of your advice, for all the late nights you spent helping me meet paper deadlines, for pushing me when I needed it and stepping back when I needed that, thank you!

A close second is Christopher Manning, who introduced me to research in natural language processing and for better or worse, knowledge base population.
Every meeting I've had with Chris, I've left with feeling deeply inspired and energized, but also disappointed that I'd but scratched the surface of his wisdom.
I am incredibly grateful to have been able to collaborate with Chris over several summers for KBP, and to have been a teaching assistant for his natural language processing class (co-taught by Richard Socher).

I have been blessed to have wonderful thesis committee members--- in addition to Percy and Chris Manning, Michael Bernstein and Chris Re's insightful feedback have made this thesis an order of magnitude better without it having to take an order of magnitude longer!

I would not be here were it not for the long line of mentors that have groomed me into the person I am today.
In chronological order, I would like to thank:
Mr.\ Derrik Mosser--- who showed me the magic of (computer) science and engineering at all of age 10 (sorry I didn't choose MIT!), 
Ragini Ma'am--- who kept that flame burning bright through high school,
Ravindran Balaraman--- my undergraduate advisor with whom I shared my favorite papers, books and ideas, 
Sriram Rajamani and Ranjita Bhagwan--- who gave me my first taste of research at Microsoft Research India,
Aditya Nori--- whose positivity, support, sponsorship and guidance I haven't the words to describe
and
Gabor Angeli--- whose terrible influence was responsible for many wonderful things.
Additionally, I would like to thank Shankar Balachandran, who made me a better human being.

I've learned so much from collaborating with amazing people who made my PhD not only more productive but ten-fold happier:
Volodymyr Kuleshov--- who's always brimming with ideas,
Sida Wang--- who I enjoyed posting up against on the basketball court as much as keeping up with on the whiteboard,
Keenon Werling--- who I had the fortune to mentor and now has the fortune to mentor me,
Ashwin Paranjape--- who's always a good sport and biased for action,
Steve Mussmann--- for his rigour without rigamarole,
Matt Lamm--- for teaching me what linguistics is all about.
I also can't thank enough everyone I had the pleasure to work with on the best KBP team ever: Chris Manning, Gabor Angeli, Melvin Johnson, Ashwin Paranjape, Yuhao Zhang, Peng Qi, Jinhao Lei, Danqi Chen, Jason Bolton, Kevin Clark, Matt Lamm, Abi See and others.
To the $\mathbb{P}\lambda$ crew: Roy Frostig, Jacob Steinhardt, Kelvin Guu, Panupong ``Ice'' Pasupat, Dan Selsam, Robin Jia, Stephen Mussmann, Pang Wei Koh, Fereshte Khani, Aditi Raghunathan, He He, Yuchen Zhang, Tatsu Hashimoto, Jonathan Berant.
To the whole Stanford NLP group--- I couldn't imagine a smarter, kinder and more fun lab to be a part of!

% friends
I would not have been able to withstand the vicissitudes of grad school were it not for an army of friends that supported me even when I had the tendency to disppear for weeks on end to try to meet a deadline:
Lavanya Jose, Ananth Raghunathan and Nikhil Handigol--- our running group was the one thing that kept me afloat during my first few years,
Vimal Jeyakumar--- for your sage advice, for your ever insightful questions and for pulling me back from the brink,
Ankita Kejriwal, Devon Chandler, Angel Chang, Manolis Saava, Irene Kaplow, Dave Held, Joe Zimmberman, Gabor Angeli, Sharon Lin--- thank you for keeping my Friday nights fun and unproductive and being just the most loving group of people I know,
Bharat Ramsundar--- for so many caffeine-fueled conversations,
Seth Werfel--- for being a co-conspirator in many things, even if they didn't work out,
Pavneet Singh--- for letting me share your dream and help bring it to life.
To the SoBay Superstars and Amazon Primers: Tilak Sharma, Shashank Shekar, Vasuki Narashimaswamy, Nishant Totla, Vaishnavi Surendra, Pranesh Srinivasan, Samhita K, Siva Ramakrishnan, Prakash Mohan, Akila Kesavaswamy, Akarsh Simha, Prateek ``Kama'' Gaur--- thanks for always being there when I needed it.
To the BBz--- Ashish ``Baba'' Kashyap, Tanmai ``Coco'' Gopal, Rikin Kacchia, Sriram ``Tehelka'' Srikant--- our goal is world domination, atleast until the winged monkeys turn on us.
To the Asha Stanford crew--- Janani Subramanian, Mohammed ``Moch'' Habibulla, Shruthi Prabhakara, Pradeep Jayaraman, Aparna Khare, Vatsal Sharan, Tanmay Chavan, Pratiksha Thaker, Neha Nayak--- thank you for helping me find meaning, hope and inspiration to serve beyond myself.

% family
To my parents, Krishna Rao Chaganty and Radha Chaganty, for their ever present, unconditional love that laid the best foundation one could hope for, my brother Aditya Chaganty for introducing me to all the things as big brothers are wont do and his wife, Spurthi Devalla, for being an elder sister to me.
To the extended family of Chagantys and Ivaturis who have been there for me throughout my life and made it that much richer.
To Harini Raghu, Raghu Padmanabhan and Aniruddh Raghu, for your love, support and well-wishes.

% maithra
Last but not least, I would like to thank Maithreyi Raghu, my highly significant other\footnote{$p < 0.005$} and my best half, whose role in my life has quickly grown from friend to family.
To Maithra: for always picking me up when I've been down, for keeping me present and for always making me smile, thank you!
